LLM-Driven CIDOC-CRM Knowledge Graph Extraction from Museum Archives

### 2025-05-05 paper/paper.tex
paper: fig ontology guided prompt
paper: figures adjustment for space, and caption

%\author{\small *No authors informations during review process.}
% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
% \author{\IEEEauthorblockN{Michael Shell}
%     \IEEEauthorblockA{School of Electrical and\\Computer Engineering\\
%         Georgia Institute of Technology\\
%         Atlanta, Georgia 30332--0250\\
%         Email: http://www.michaelshell.org/contact.html}
%     \and
%     \IEEEauthorblockN{Homer Simpson}
%     \IEEEauthorblockA{Twentieth Century Fox\\
%         Springfield, USA\\
%         Email: homer@thesimpsons.com}
%     \and
%     \IEEEauthorblockN{James Kirk\\ and Montgomery Scott}
%     \IEEEauthorblockA{Starfleet Academy\\
%         San Francisco, California 96678--2391\\
%         Telephone: (800) 555--1212\\
%         Fax: (888) 555--1212}}

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=3in]{assets/ontology}
    \caption{CIDOC-CRM Ontology}
    \label{fig_ontology}
\end{figure}

@@

@@

\begin{table}[h]
    \centering
    \caption{Models used for Knowledge Graph Generation} % Updated caption slightly
    \label{tab:model_deployment}
    \begin{tabular}{ll}
        \hline
        Model        & Deployment            \\
        \hline
        Qwen 2.5 3B  & Ollama on RTX 3060    \\
        Llama 3.2 3B & Ollama on RTX 3060    \\
        Qwen 2.5 7B  & LM Studio on RTX 5090 \\
        Llama 3.1 8B & LM Studio on RTX 5090 \\
        DeepSeek V3  & DeepSeek Platform     \\
        DeepSeek R1  & DeepSeek Platform     \\
        \hline
    \end{tabular}
\end{table}

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=3in]{assets/graph-qwen3b-adze}
    \caption{Ontology-guided graph from text "Adze" - Qwen2.5 3B}
    \label{fig_graph_qwen3b_adze}
\end{figure}

\begin{figure}[!t]
    \centering
    \includegraphics[width=3in]{assets/graph-r1-adze}
    \caption{Ontology-guided graph from text "Adze" - DeepSeek R1}
    \label{fig_graph_r1_adze}
\end{figure}

>>>>

\author{\small *No authors' information during review process.}
% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
% \author{\IEEEauthorblockN{Michael Shell}
%     \IEEEauthorblockA{School of Electrical and\\Computer Engineering\\
%         Georgia Institute of Technology\\
%         Atlanta, Georgia 30332--0250\\
%         Email: http://www.michaelshell.org/contact.html}
%     \and
%     \IEEEauthorblockN{Homer Simpson}
%     \IEEEauthorblockA{Twentieth Century Fox\\
%         Springfield, USA\\
%         Email: homer@thesimpsons.com}
%     \and
%     \IEEEauthorblockN{James Kirk\\ and Montgomery Scott}
%     \IEEEauthorblockA{Starfleet Academy\\
%         San Francisco, California 96678--2391\\
%         Telephone: (800) 555--1212\\
%         Fax: (888) 555--1212}}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=3.3in]{assets/ontology}
    \caption{Ontology derived from CIDOC-CRM}
    \label{fig_ontology}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=3.5in]{assets/ontology_guided}
    \caption{Ontology-guided triplet extraction using single-stage prompting}
    \label{fig_ontology_guided}
\end{figure}

@@

\begin{table}[h]
    \centering
    \caption{Models used for Knowledge Graph Generation}
    \label{tab:model_deployment}
    \begin{tabular}{ll}
        \hline
        Model        & Deployment            \\
        \hline
        Qwen 2.5 3B  & Ollama on RTX 3060    \\
        Llama 3.2 3B & Ollama on RTX 3060    \\
        Qwen 2.5 7B  & LM Studio on RTX 5090 \\
        Llama 3.1 8B & LM Studio on RTX 5090 \\
        DeepSeek V3  & DeepSeek Platform     \\
        DeepSeek R1  & DeepSeek Platform     \\
        \hline
    \end{tabular}
\end{table}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=3.5in]{assets/graph-qwen3b-adze}
    \caption{Graph extracted from text "Adze" with ontology - Qwen2.5 3B}
    \label{fig_graph_qwen3b_adze}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=3.5in]{assets/graph-r1-adze}
    \caption{Graph extracted from text "Adze" with ontology - DeepSeek R1}
    \label{fig_graph_r1_adze}
\end{figure}
